### 2022-05-06 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@a6ff52cba4a8aff6ea61aa5a49940c782705e61e 🚀
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@b13788b40ddec32d74b5c7534b57b6aecf35d419 🚀

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}
\begin{document}
\raggedright
\thispagestyle{empty}
{\Large\bfseries\sffamily Building a better metaweb: predicting
spatially and temporally explicit alpine plant-pollinator interaction
networks}
\vskip 5em

@@

Species interactions are important. It is ultimately interactions
between individuals of different species that drive the structure,
dynamics, and persistence of ecosystems, and the abundance and diversity
of the species within them. Plant-pollinator interactions specifically
drive the function and persistence of ``architecture of biodiversity''
(Bascompte \& Jordano 2007). However, we are far from a robust
understanding of plant-pollinator networks. This is because sampling
interactions is costly. Interactions vary in space and time (Poisot
\emph{et al.} 2015)---particularlly relevent in this system {[}Paul
phenology cite{]}. This is why there is interest in using models to
predict interactions from sparse data (\textbf{Strydom2021?}). In this
paper, we combine several datasets, each spanning several years, to
produce spatially and temporally explicit predictions of the bumblebee
(genus \emph{Bombus}) and wildflower pollination network across the
state of Colorado.

@@

\textbf{\emph{Concept Fig}}

@@

>>>>

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}
\begin{document}
\raggedright
\thispagestyle{empty}
{\Large\bfseries\sffamily Building a better metaweb: predicting
spatiotemporally explicit plant-pollinator networks}
\vskip 5em

@@

Species interactions are important. It is ultimately interactions
between individuals of different species that drive the structure,
dynamics, and persistence of ecosystems, and the abundance and diversity
of the species within them. Plant-pollinator interactions specifically
drive the function and persistence of ``architecture of biodiversity''
(Bascompte \& Jordano 2007). However, we are far from a robust
understanding of plant-pollinator networks. This is because sampling
interactions is costly. Interactions vary in space and time (Poisot
\emph{et al.} 2015)---particularlly relevent in this system (CaraDonna
\emph{et al.} 2014). This is why there is interest in using models to
predict interactions from sparse data (\textbf{Strydom2021?}). In this
paper, we combine several datasets, each spanning several years, to
produce spatially and temporally explicit predictions of the bumblebee
(genus \emph{Bombus}) and wildflower pollination network across the
state of Colorado.

@@

\begin{figure}
\centering
\includegraphics{./figures/concept.png}
\caption{todo}
\end{figure}

@@

\leavevmode\hypertarget{ref-CaraDonna2014ShiFlo}{}%
CaraDonna, P.J., Iler, A.M. \& Inouye, D.W. (2014). Shifts in flowering
phenology reshape a subalpine plant community. \emph{Proceedings of the
National Academy of Sciences}, 111, 4916--4921.
